Exploring Design Space for Differentially Private Bayesian Inference

### 2018-12-28 ICML2019/main.tex
update experiments

\subsection{Exponential Mechanism Family}
In this section, we explore the exponential mechanism family: $\expmech{}{\cdot}{\cdot}{\cdot}$ by considering Hellinger distance metrics and different sensitivities.

@@

\subsubsection{Standard Exponential Mechanism with Hellinger Metric}
Standard exponential mechanism $\expmech{}{x}{u}{\candidateset}$ samples an element from the candidate set $\candidateset = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 GS})$:
\begin{equation*}
\underset{z \thicksim \expmech{}{x}{u}{\candidateset} }{Pr}[z=r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 GS})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 GS})},
\end{equation*}
where $u(x,r)$ is the Hellinger scoring function over candidates, $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity of the scoring function (i.e. the global sensitivity of the Bayesian inference w.r.t the Hellinger distance), calculated by:
\begin{equation*}
GS = 
\max_{\{|\dataobs,\dataobs'| \leq 1;\dataobs,\dataobs'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}
|\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
\end{equation*}

@@

\subsubsection{Exponential Mechanism with Hellinger Metric and Local Sensitivity}
\label{subsec_emls}
% \subsubsection{Mechanism Set up}
Exponential mechanism with local sensitivity $\expmech{local}{x}{u}{\candidateset}$ share the same candidate set and utility function as it with standard exponential mechanism. This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})$:
\begin{equation*}
\underset{z \thicksim \expmech{local}{x}{u}{\candidateset}}{\Pr}[z=r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 LS(\dataobs)})},
\end{equation*}

@@

\subsection{Privacy of Exponential Mechanism Family}
\subsubsection{$\expmech{}{}{}{}$ $\epsilon-$Differential Privacy}
Standard exponential mechanism is $\epsilon-$differential privacy by \cite{dwork2014algorithmic}.

\subsubsection{$\expmech{local}{}{}{}$ non-Differential Privacy}
Exponential mechanism with local sensitivity non-differential privacy.

@@

Specifically, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer(\dataobs)$:
\begin{equation*}
\begin{split}
LS(\dataobs) 
  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs)) - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\} \\
  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\}.
\end{split}
\end{equation*}

@@

\begin{figure}
\begin{center}
\centering
  \subfigure[2 dimensions with data size $600$]{
    \includegraphics[width=0.45\textwidth]{theory_2d.eps}
  \label{subfig_theory_2d}
  }
  \subfigure[3 dimensions with data size $600$]{
    \includegraphics[width=0.45\textwidth]{theory_3d.eps}
  \label{subfig_theory_3d}
  }
\caption{The theory probabilities of outputting candidates in certain distance from true posterior, with balanced data set and parameters $\epsilon = 1.0$}
\label{fig_theory}
\end{center}
\end{figure}

In Fig. \ref{fig_theory}, candidates of smaller distance from true posterior can be outputted by $\hexpmech$ (in blue line) with larger probability than by baseline Laplace mechanism (in green line). This means $\hexpmech$ can produce good results with larger probability than baseline mechanism. However, the improved Laplace mechanism represented by red line can produce good results with probability higher than $\hexpmech$. It outperforms $\hexpmech$.

\begin{figure}
\begin{center}
\centering
  \subfigure[2 dimensions of data size 1000]{
    \includegraphics[width=0.42\textwidth]{epsilon5_2d_1000.eps}
  \label{subfig_theory_2d}
  }
  \subfigure[2 dimensions of data size 10000]{
    \includegraphics[width=0.42\textwidth]{epsilon5_2d_10000.eps}
  \label{subfig_theory_3d}
  }
\caption{The theory probabilities of outputting candidates in certain distance from true posterior, with balanced data set and parameters $\epsilon = 5.0$}
\label{fig_theory_epsilon}
\end{center}
\end{figure}
Increasing the privacy bound $\epsilon$, we get theoretical results as in Fig. \ref{fig_theory_epsilon}. In 2 dimensions, we can perform better than Laplace mechanisms.

@@

\begin{figure}
\begin{center}
\centering
    \includegraphics[width=0.45\textwidth]{sampling_2d.eps}
\caption{Increasing data size with prior $\betad(1,1)$, balanced datasets and parameters $\epsilon = 1.0$}
\label{fig_vs_datasize_2d}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\centering
\subfigure[Increasing data size with $\dirichlet(1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$]
{
        \includegraphics[width=0.42\textwidth]{sampling_3d.eps} 
        \label{fig_vs_datasize_3d}
}
\subfigure[Increasing data size with $\dirichlet(1,1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$]
{
     \includegraphics[width=0.42\textwidth]{sampling_4d.eps} 
\label{fig_vs_datasize_4d}
}
\end{center}
\end{figure}

% \begin{figure}[ht]
% \begin{center}
% \centering

% \end{center}
% \end{figure}

>>>>

\subsection{Exponential Mechanism Family}
In this section, we explore the exponential mechanism family: $\expmech(\cdot,\cdot,\cdot)$ by considering Hellinger distance metrics and different sensitivities.

@@

\subsubsection{Standard Exponential Mechanism with Hellinger Metric}
Standard exponential mechanism $\expmech(x,u,\candidateset)$ samples an element from the candidate set $\candidateset = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 GS})$:
\begin{equation*}
\underset{z \thicksim \expmech(x,u,\candidateset) }{Pr}[z=r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 GS})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 GS})},
\end{equation*}
where $u(x,r)$ is the Hellinger scoring function over candidates, $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity of the scoring function (i.e. the global sensitivity of the Bayesian inference w.r.t the Hellinger distance), calculated by:
\begin{equation*}
GS = 
\max_{\{|\dataobs,\dataobs'| \leq 1;\dataobs,\dataobs'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}
|\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
\end{equation*}

@@

\subsubsection{Exponential Mechanism with Hellinger Metric and Local Sensitivity}
\label{subsec_emls}
% \subsubsection{Mechanism Set up}
Exponential mechanism with local sensitivity $\lexpmech(x,u,\candidateset)$ share the same candidate set and utility function as it with standard exponential mechanism. This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})$:
\begin{equation*}
\underset{z \thicksim \expmech{local}{x}{u}{\candidateset}}{\Pr}[z=r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 LS(\dataobs)})},
\end{equation*}

@@

\subsection{Privacy of Exponential Mechanism Family}
\subsubsection{$\expmech$ $\epsilon-$Differential Privacy}
Standard exponential mechanism is $\epsilon-$differential privacy by \cite{dwork2014algorithmic}.

\subsubsection{$\lexpmech$ non-Differential Privacy}
Exponential mechanism with local sensitivity non-differential privacy.

@@

Specifically, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer(\dataobs)$:
\begin{equation*}
\begin{split}
LS(\dataobs) 
  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs)) \\
  & - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\} \\
  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\}.
\end{split}
\end{equation*}

@@

\begin{figure}
\begin{center}
\centering
  \subfigure[2 dimensions, data size $600$]{
    \includegraphics[width=0.22\textwidth]{theory_2d.eps}
  \label{subfig_theory_2d}
  }
  \subfigure[3 dimensions, data size $600$]{
    \includegraphics[width=0.22\textwidth]{theory_3d.eps}
  \label{subfig_theory_3d}
  }
\caption{The theory probabilities of outputting candidates in certain distance from true posterior, with balanced data set and parameters $\epsilon = 1.0$}
\label{fig_theory}
\end{center}
\end{figure}

Candidates of smaller distance from true posterior are considered to be good results, which can result in good accuracy. From Fig. \ref{fig_theory}, it can be derived that all these mechanisms (except standard exponential mechanism $\expmech$ in green line) can output good results with larger probability. The $\lexpmech$ can output good results with higher probability than others, but $\lexpmech$ is non-private. For these are $\epsilon -$differentially private, the improved laplace mechanism $\ilapmech$ with $\ell_1$ norm metric can produce good results with higher probability, i.e., perform better in terms of accuracy than others. As the dimension increases from 2 to 3, mechanisms' behavior remain the same.

\begin{figure}
\begin{center}
\centering
  \subfigure[data size 1000]{
    \includegraphics[width=0.22\textwidth]{epsilon5_2d_1000.eps}
  \label{subfig_theory_2d}
  }
  \subfigure[data size 10000]{
    \includegraphics[width=0.22\textwidth]{epsilon5_2d_10000.eps}
  \label{subfig_theory_3d}
  }
\caption{The theory probabilities of outputting candidates in certain distance from true posterior, with balanced data set and parameters $\epsilon = 5.0$, in 2 dimensions}
\label{fig_theory_epsilon}
\end{center}
\end{figure}

Increasing the privacy bound $\epsilon$, we get theoretical results as in Fig. \ref{fig_theory_epsilon} in 2 dimensions. The $\lexpmech$ is still the one with the best accuracy, but it is non-private. However, the $\lapmech$ and $\ilapmech$ having the similar performance, and $\hexpmech$ can produce the correct posterior with higher probability than the others. And the standard exponential mechanism $\expmech$ is still the worst one.

@@

\begin{figure}[ht]
\begin{center}
\centering
\subfigure[Increasing data size with prior $\betad(1,1)$, balanced datasets and parameters $\epsilon = 1.0$]
{ \includegraphics[width=0.4\textwidth]{sampling_2d.eps}
\label{fig_vs_datasize_2d}
}

\subfigure[Increasing data size with $\dirichlet(1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$]
{
  \includegraphics[width=0.4\textwidth]{sampling_3d.eps} 
  \label{fig_vs_datasize_3d}
}
\subfigure[Increasing data size with $\dirichlet(1,1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$]
{
  \includegraphics[width=0.4\textwidth]{sampling_4d.eps} 
  \label{fig_vs_datasize_4d}
}
\end{center}
\end{figure}
